Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-07 paper/SI.tex
Add results for the charge density calculations

\section{Measurement of charge carrier density of patterned graphene}
\label{sec:charge-dens}
The intrinsic charge carrier density of graphene was measured using a 
field electron transistor (FET) in air with a 300nm SiO$_2$ as a gate.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/charge-dens.png}
  \caption{The I$_{SD}$ as a function of V$_G$. The electron mobility of xyz is extracted from the graph, which very similar to the 
  intrinsic charge carrier density of unpatterned graphene (See Main Text).}
  \label{fig:charge-dens}
\end{figure}

>>>>

\section{Measurement of charge carrier density of patterned graphene}
\label{sec:charge-dens}
The intrinsic charge carrier density of graphene was measured using a
field electron transistor (FET) in air with a 300nm SiO$_2$ as a
gate. The device setup is shown in \Fig{} \ref{fig:charge-dens}a,
where the source and drain electrodes were deposited onto the PG
sample transfered onto 300nm SiO$_2$ on doped Silicon. The
characteristic drain-source current $I_{\mathrm{DS}}$ as a function of
$V_{\mathrm{G}}$ is shown in \Fig{} \ref{fig:charge-dens}. The
charge-neutral point gate voltage $V_{\mathrm{CNP}}$ is measured to be 2.8 V.
Using the capacitance of the SiO$_{2}$ dielectric, we an intrinsic
charge density of $\sim{}$1.4$\times$10$^{11}$
\textit{e}$\cdot$cm$^{-2}$, and a shift in the PG's Fermi level by
$\sim{}$48 meV, which is negligible compared with the gate-induced
charge density in our experiments. Therefore, the assumption that the
PG sample is intrinsic without gating, is justified.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gr-transistor.pdf}
  \caption{Characterization of the intrinsic charge density of the PG
    sample using field effect transistor. \textbf{a}. The setup of the
    PG-FET. \textbf{b}. The I$_{\mathrm{DS}}$ as a function of
    $V_{\mathrm{G}}$. The charge neutral point gate voltage is
    determined as $\sim{}$2.8 V, corresponding to an intrinsic charge
    density of $\sim{}$1.4$\times$10$^{11}$
    \textit{e}$\cdot$cm$^{-2}$, which is negligible compared with the
    gate-induced charges.}
  \label{fig:charge-dens}
\end{figure}

### 2019-01-07 paper/paper.tex
Add results for the charge density calculations

$\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
\phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
function. The properties of the PG samples fabricated is close to
intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
to be XXX $e \cdot$cm$^{-2}$, corresponding to a work function
difference of XXX meV from graphene's Dirac point (details see
Supplementary Section S5), much smaller than the
$\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
simplification that the charge neutrality point of graphene coincides
with the Dirac point at $V_{\mathrm{G}}$ = 0. The elementary
electronic properties of graphene give:

>>>>

$\Delta \phi_{\mathrm{G}} = \phi_{\mathrm{G}}(V_{\mathrm{g}}) -
\phi_{\mathrm{G}}(V_{\mathrm{g}}=0)$ is the change of graphene’s work
function. The properties of the PG samples fabricated is close to
intrinsic graphene, with charge density at $V_{\mathrm{G}}=0$ measured
to be 1.4$\times$10$^{11}$ \textit{e}$\cdot$cm$^{-2}$, corresponding
to a work function difference of 48 meV from graphene's Dirac point
(details see Supplementary Section S5), much smaller than the
$\Delta \phi_{\mathrm{G}}$ induced by gating.  Therefore we adapt the
simplification that the charge neutrality point of graphene coincides
with the Dirac point at $V_{\mathrm{G}}$ = 0. The elementary
electronic properties of graphene give:
